Millions of Type Errors

### 2023-06-02 oopsla23/paper.tex
CodeTooComplex notes

\subsection{Code Too Complex}

The (example) code is NEVER too complex.

@@

Error counts per-project and per-module include syntax errors.
Problematic, because syntax errors are uninteresting (easy to fix),
but common, which makes it likely that our per-keystroke telemetry will record them.
Edit region has specific counts.
Next time, we should do that for the other aggregates.

@@

>>>>

\subsection{Dead Ends: Too Complex}

The typechecker has two internal limits regarding the problems it will attempt
to solving.
Hitting a limit triggers either a \code{CodeTooComplex} or
\code{UnificationTooComplex} error.
A casual user should never see these errors.

Based on the data, these errors are indeed extremely rare.
Out of 1.5M telemetry records, only 11 report any \code{TooComplex} errors.
These records came from three sessions (possibly by a single user), and each
record counted at most 4 \code{CodeTooComplex} errors and zero
\code{UnificationTooComplex} errors.
There is no evidence to suggest that the limits are too strict or that the
typechecker should improve.

@@

Error counts per-project and per-module include syntax errors.
Problematic, because syntax errors are uninteresting (easy to fix),
but common, which makes it likely that our per-keystroke telemetry (1/2k) will record them.
Edit region has specific counts.
Next time, we should do that for the other aggregates.

@@

%% zfstt-ieeesensors-2022
